--- 
title: "Thermodynamics One"
subtitle: "Semester Projects"
author: "marcus ashford, phd"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
output:
  bookdown::tufte_html_book:
    includes: 
      in_header: preamble.html
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---


# Prerequisites {-}


\begin{equation}
x^2 - \frac{y}{4}
\end{equation}




## ORC

## Home energy audit for parent aand child

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$ or   \ce{H2SO4} .

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
